sensiAnPaper1All

### 2016-06-15 inst/documents/sensiAnPaper1All.Rmd
new runs

This breaks down into these subsidiary quetsions :
1. Under which scenarios is the time to resistance for either insecticide quicker for

@@

  ## save results objects as rda for re-use
  save(listOutMix, file=paste0(outFolder,'listOutMix_unequal.rda'))
  save(listOutI1, file=paste0(outFolder,'listOutI1_unequal.rda'))
  save(listOutI2, file=paste0(outFolder,'listOutI2_unequal.rda'))

  # save(listOutMix, file=paste0(outFolder,'listOutMix_ex2_10000.rda'))
  # save(listOutI1, file=paste0(outFolder,'listOutI1_ex2_10000.rda'))
  # save(listOutI2, file=paste0(outFolder,'listOutI2_ex2_10000.rda'))

>>>>

@@

  ## save results objects as rda for re-use

  save(listOutMix, file=paste0(outFolder,'listOutMix_rr_10.rda'))
  save(listOutI1, file=paste0(outFolder,'listOutI1_rr_10.rda'))
  save(listOutI2, file=paste0(outFolder,'listOutI2_rr_10.rda'))
